\vspace{-1in}Identity signaling model progress

### 2020-02-26 reports/Progress-2-26.tex
report and NB updated with min. frac. 0.25

\usepackage{caption}
\usepackage{booktabs}
\usepackage{pslatex}
\usepackage{apacite}
\usepackage{subcaption}
\usepackage{pgfplots}
\usepackage{wrapfig}
\usepackage[english]{babel}
\usepackage{lmodern}
\usepackage{setspace}
\doublespace
% \usepackage{url}
\usepackage{bigfoot}
\usepackage[export]{adjustbox}
\setlength\intextsep{0pt}

@@

\begin{document}
\maketitle

@@

So far in these results I tested the case where a 10\% of all agents have
the minority trait, $+1$ in the first trait vector position. 
The other 90\% have the majority trait, $-1$ in the first trait vector position.

@@

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/covert_series_majority.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/covert_series_minority.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \caption{Mean timeseries of the evolution of covert signaling in the
    majority (a) and minority (b) populations.}
  \label{fig:regressions}
\end{figure}

@@

@@

@@

>>>>

\usepackage{caption}
\usepackage{booktabs}
\usepackage{pslatex}
\usepackage{apacite}
\usepackage{subcaption}
\usepackage{pgfplots}
\usepackage{wrapfig}
\usepackage[english]{babel}
\usepackage{lmodern}
\usepackage{setspace}
\doublespace
% \usepackage{url}
\usepackage{bigfoot}
\usepackage[export]{adjustbox}
\setlength\intextsep{0pt}
\hypersetup{linktocpage}

@@

\begin{document}
\maketitle
\tableofcontents

@@

So far in these results I tested the case where a 10\% or 25\% of all agents have
the minority trait, $+1$ in the first trait vector position. 
The other 90\% or 75\% have the majority trait, $-1$ in the first trait vector position.

@@

\subsubsection{Fraction of minorities = 0.10}
\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/covert_series_majority.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/covert_series_minority.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \caption{Mean timeseries of the evolution of covert signaling in the
    majority (a) and minority (b) populations.}
  \label{fig:}
\end{figure}

@@

\subsubsection{Fraction of minorities = 0.25}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/covert_series_majority_025.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/covert_series_minority_025.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \caption{Mean timeseries of the evolution of covert signaling in the
    majority (a) and minority (b) populations.}
  \label{fig:regressions}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/majority_signalers_025.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/minority_signalers_025.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \caption{Proprtion of covert signalers for different parameter settings in the
    majority (a) and minority (b) populations.}
  \label{fig:regressions}
\end{figure}

\begin{figure}[H]
  \centering
    \includegraphics[width=0.6\textwidth]{Figures/covert_signalers_diff_025.pdf}
  \caption{Difference between proportion of covert signalers in the minority 
    and majority populations. When cost of disliking is high and homophily is 
    low, more minority agents are covert signalers than majority agents,
    proportionally. An increase in homophily enables minority agents to 
    find one another more easily, so overt signaling, which reaches more of
    the population, is advantageous.
  }
  \label{fig:}
\end{figure}

@@

\subsubsection{Fraction of minorities = 0.10}

@@

\subsubsection{Fraction of minorities = 0.25}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/churlish_series_majority_025.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/churlish_series_minority_025.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \caption{Mean timeseries of the evolution of churlish receiving in the
    majority (a) and minority (b) populations.}
  \label{fig:regressions}
\end{figure}

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/majority_receivers_025.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{Figures/minority_receivers_025.pdf}
    \caption{}
    \label{fig:}
  \end{subfigure}
  \caption{Proprtion of churlish receivers for different parameter settings in the
    majority (a) and minority (b) populations.}
  \label{fig:regressions}
\end{figure}

\begin{figure}[H]
  \centering
    \includegraphics[width=0.6\textwidth]{Figures/churlish_receivers_diff_025.pdf}
  \caption{Difference between proportion of churlish receivers in the minority 
    and majority populations. Here the dependence is primarily on homophily.
    If homophily is too low, the minority population cannot interact often
    enough with their in-group, and so must adopt a non-churlish stance towards
    others in order to not suffer cost of disliking penalties. Once the minority
    can reliably find its in-group members (increasing homophily) the minority
    can afford to assume they dislike others, since by and large they dislike
    the majority.
  }
  \label{fig:}
\end{figure}
